
\chapter{Work Plan} \label{ch-1}

\section{Research}

The future work for research is structured into 2 main parts.

\begin{enumerate}
    \item Similarities between Arms.\\
    First, based on the current research, I am interested in exploring the similarities between arms for bandits problems. Two directions for exploring this topic can go in parallel. 
    \begin{itemize}
        \item Extend the current work (Median-based UCB) to the graph/contextual setting.
        \item Using bandits to recommend DNA sequence for synthetic biology design.
    \end{itemize}
    
    \item Summary Statistics for Bandits.\\
    One interesting question is that, except median, what other summary statistics can be considered as summarising the reward distribution, and what kind of summary statistics suits for what the user requirements? For example, taking risk into consideration. Then whether we can derive a corresponding confidence width term in terms of these statistics?  
    
\end{enumerate}

The final goal is to consider different summary statistics for both independent and dependent arms in the bandit setting.



\section{Internship}

About: similarities between arms in bandits\\
Possible topic: graph bandits; contextual bandits\\
To be decided.

\section{Tutoring and Courses}

Tutoring List: Statistical Machine Learning.\\
Course List: Graph Course; Biology Course; Reinforcement Learning Course.

\section{Timeline}

I commenced my Ph.D. from 2018/8.

\begin{itemize}
    \item 2019/11 - 2020/2: \\
    SynBio with bandits algorithms with existing data (hopefully novelty in designing models for identifying similarity between arms, or in embedding sequences).\\
    Target: ICML (Deadline 2020/2/7)
    \item 2019/11 - 2020/5: \\
    Extend the M-UCB to contextual/graph bandit model (considering risk for contextual models).\\
    Target: NeuIPS (Deadline in May 2020)
    \item 2019/11 - 2020/6: \\
    SynBio with bandits algorithms with new data (hopefully help to identify some interesting biology properties) \\
    Target: Biology Journal (depends on how collaborators think)
    \item 2020/6 - 2020/12:\\
    2020/6/3 - 202/6/5: AISTATS (depends on whether get accepted)\\
    2020/6/12 - 2020/6/18: ICML2020\\
    2020/6/28 - 2020/7/10: MLSS in Germany\\
    2020/7 - : internship (to be decided, and hopefully one paper during internship)\\
    \item 2021/1 -2021/6:\\
    Depends on the research progress. But the current plan is to research on different summary statistics for bandits, for both dependent and independent arm cases. 
    Combine the AISTATS, NeurIPS, and summary statistics material into one paper.\\
    Target: JMLR
    
    
    
    
\end{itemize}